Peer influences in air travel behavior: A social autoregressive analysis

### 2015-03-20 article.Rmd
Change from Rda to rds saving format.

The online survey instrument was adapted from Wall et al (2014), and
contains three principal components.  For a detailed description of the
variables collected, refer to Wall et al. (2014).  The first component
collected respondents’ air travel information from the past year – this includes
a list of trips taken with origin and destination airports for round-trip,
multi-destination, and one-way travel.  The second component collected
socio-demographic information, including age, gender, income, education level,
citizenship, occupation, and race.  The third component asked respondents to log
in to their Facebook accounts, and the survey automatically collected data
contained in the respondent's profile and friends list via the Facebook
application programming interface (API).  This data included the hometown city
and current city locations of the respondents, and also that of the respondents’
friends.  The program also collected an encrypted (one way hash) version of the
Facebook ID for all respondents and their friends.  This ensured subject
anonymity while simultaneously allowing observations regarding 1) which
respondents were friends with each other, and 2) how many friends respondents
have in common, 3) identifying and limiting the potential for duplicate
respondents.

>>>>

The online survey instrument was adapted from Wall et al (2014), and
contains three principal components.  For a detailed description of the
variables collected, refer to Wall et al. (2014).  The first component
collected respondents’ air travel information from the past year – this includes
a list of trips taken with origin and destination airports for round-trip,
multi-destination, and one-way travel.  The second component collected
socio-demographic information, including age, gender, income, education level,
citizenship, occupation, and race.  The third component asked respondents to log
in to their Facebook accounts, and the survey automatically collected data
contained in the respondent's profile and friends list via the Facebook
application programming interface (API).  This data included the hometown city
and current city locations of the respondents, and also that of the respondents’
friends.  The program also collected an encrypted (one way hash) version of the
Facebook ID for all respondents and their friends.  This ensured subject
anonymity while simultaneously allowing us to observe which
respondents were friends with each other, as well as how many friends respondents
have in common even if those common friends did not participate in the survey.

```{r load_user}
user <- readRDS("data/clean/user.rds")
trips <- readRDS("data/clean/trips.rds")
friends <- readRDS("data/clean/friends.rds")
```
